### 2023-04-27 main.tex
Explicitly defined backend for biblatex as biber
Change name of bibliography to references
Changed caption font size to small to better fit large figures on pages
Updated chapter 2 title

% Chapter and figure formatting
\usepackage{longtable}
\usepackage{titlesec}  % Modify chapter title format
\titleformat{\chapter}[display]% Shape (chapter label in separate paragraph)
                      {\bfseries\Large}% Format
                      {\MakeUppercase{\chaptertitlename} \thechapter}% Label
                      {0in}% Sep
                      {}% Before code
                      []% After code
\setcounter{tocdepth}{1}  % Only number divisions to section
\usepackage[labelfont=bf, labelsep=period]{caption}
\renewcommand{\thefigure}{\thechapter.\arabic{figure}}

% References
\usepackage[doi=false,url=false, style=nature]{biblatex}
\addbibresource{refs.bib}
\usepackage{hyperref}

@@

\chapter{Evolutionary analyses of IDRs reveal conserved features}
\label{chapter:2}
\graphicspath{{chapter2/figures/}}
\input{chapter2/chapter2.tex}

@@

\printbibliography[heading=bibintoc]

>>>>

% Chapter and figure formatting
\usepackage{longtable}
\usepackage{titlesec}  % Modify chapter title format
\titleformat{\chapter}[display]% Shape (chapter label in separate paragraph)
                      {\bfseries\Large}% Format
                      {\MakeUppercase{\chaptertitlename} \thechapter}% Label
                      {0in}% Sep
                      {}% Before code
                      []% After code
\setcounter{tocdepth}{1}  % Only number divisions to section
\usepackage[font=small, labelfont=bf, labelsep=period]{caption}
\renewcommand{\thefigure}{\thechapter.\arabic{figure}}

% References
\usepackage[backend=biber, style=nature, doi=false, url=false]{biblatex}
\addbibresource{refs.bib}
\usepackage{hyperref}

@@

\chapter{Evolutionary analyses of IDRs reveal patterns of conserved features}
\label{chapter:2}
\graphicspath{{chapter2/figures/}}
\input{chapter2/chapter2.tex}

@@

\printbibliography[heading=bibintoc, title=References]  % bibintoc == put in table of contents
